Tables

### 2019-04-16 code/figures.rmd
Added plot code for tau2 densitites +  'summarizer' function as sourced

```{r transform_df}
#Transform effect sizes to raw correlations
#'transform_MA' is a sourced function
res <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(transform_MA, .id = "effect") #apply function and transform back from list to dataframe

```{r MA_df}
summarizer <- function(x){#Z-transformation not recommended by Jacobs and Viechtbauer (2017) for biserial correlations, p. 176
  fitr <- rma(yi = x$r, vi = x$vi, data = x) #rma for biserial and pearson correlations (distinct per effect!)
  data.frame(r = fitr$b[[1]], tau2r = fitr$tau2, I2 = fitr$I2, H2trunc = fitr$H2, H2 = fitr$QE / (fitr$k - 1)) 
}
#Default method of metafor for calculating H2 is truncated at one. Alternative method for calculating H2 provides information also on excessive homogeneity, i.e, less variability than expected by chance (that is, does not have a lower limit of 1). This method approximates H2 as if we were using the Dersimonian and Laird estimate of tau2, although we use REML. See Higgins & Thompson, 2002 and ?print.rma.uni.

#Higgins, J., & Thompson, S. G. (2002). Quantifying heterogeneity in a meta-analysis. Statistics in medicine, 21(11), 1539-1558.

res2 <- res %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(summarizer, .id = "effect") %>% 
  mutate(r = abs(r)) #Absolute values since we are interested in effect size rather than direction
```

@@

cor.test(res2$tau2r, res2$r) #pearson tau2

tau2_fit <- summary(lm(tau2r ~ r, data = res2))

@@

```{r r_vs_tau2, fig.asp = 0.618, cache = TRUE}
r_tau2 <- ggplot(res2, aes(x = r, y = tau2r)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = expression(paste("Biserial correlation ", italic(r))))

@@

```{r Density_plot, fig.asp= 0.618, cache = TRUE}
dens <- readRDS("../data/power_simulation_results.RDS")
names(dens) <-  sort(unique(dat$effect))

@@

ggplot(I2_dist, aes(x = I2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_fill_brewer(palette = "Dark2",
                    breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                    labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
                        breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_color_brewer(palette = "Dark2", 
                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  theme(legend.position = c(0.85, 0.71),
        legend.background = element_rect(linetype = "solid", color = "black")) +
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(I^2," index", sep = ""))) +
  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))

#ggsave("../figures/density-I2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
```

>>>>

```{r transform_effect_and_compute_rma}
#Transform effect sizes to raw correlations
#'transform_MA' is a sourced function
res <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(transform_MA, .id = "effect") #apply function and transform back from list to dataframe

#compute random effect meta-analysis of transformed effects
#'summarizer' is a sourced function
res2 <- res %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(summarizer, .id = "effect") %>% 
  mutate(r = abs(r)) #Absolute values since we are interested in effect size rather than direction
```

@@

cor.test(res2$tau2, res2$r) #pearson tau2

tau2_fit <- summary(lm(tau2 ~ r, data = res2))

@@

```{r r_vs_tau2, fig.asp = 0.618, cache = TRUE}
r_tau2 <- ggplot(res2, aes(x = r, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = expression(paste("Biserial correlation ", italic(r))))

@@

```{r Density_plot, fig.asp= 0.618, cache = TRUE}

#1) I2 plot----
dens <- readRDS("../data/power_simulation_results.RDS")
names(dens) <-  sort(unique(dat$effect))

@@

I2_plot <- ggplot(I2_dist, aes(x = I2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_fill_brewer(palette = "Dark2",
                    breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                    labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
                        breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_color_brewer(palette = "Dark2", 
                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  theme(legend.position = c(0.85, 0.71),
        legend.background = element_rect(linetype = "solid", color = "black")) +
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(I^2," index", sep = ""))) +
  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))

#ggsave("../figures/density-I2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())

#2) tau2 plot----

dens_tau2 <- readRDS("../data/biserial_simulation_results.RDS")
names(dens_tau2) <-  sort(unique(dat$effect))

#Simulated data at various heterogeneity levels, prep for plotting
tau2_dist <- dens_tau2 %>% 
  bind_rows(.id = "effect") %>% 
  rename(Heterogeneity = tau_index) %>% 
  mutate(Heterogeneity = recode(Heterogeneity,
                            '1' = "Zero",
                            '2' = "Small",
                            '3' = "Medium",
                            '4' = "Large"),
         Heterogeneity = as.factor(Heterogeneity))

#Observed tau22 estimates, i.e, results from main table, see table.rmd
#Effects estimated with sourced function 'summarizer'
observed <- dat %>% 
  split(.$effect) %>%  
  map_dfr(summarizer, .id = "effect") %>% 
  select(effect, tau2 = tau2) %>%
  mutate(Heterogeneity = "Observed")

tau2_plot <- ggplot(tau2_dist, aes(x = tau2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_fill_brewer(palette = "Dark2",
                    breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                    labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
                        breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_color_brewer(palette = "Dark2", 
                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  theme(legend.position = c(0.85, 0.71),
        legend.background = element_rect(linetype = "solid", color = "black")) +
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(italic(tau)^2," index", sep = ""))) +
  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))

#ggsave("../figures/density-tau2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())

#3) combine I2-tau2-density-plots----

densities <- plot_grid(I2_plot, tau2_plot, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
densities
#save_plot("../figures/densities_het.png", densities,
#          nrow = 2, base_height = 5, base_width = 5, dpi = 600)

### 2019-04-16 code/tables.rmd
Added plot code for tau2 densitites +  'summarizer' function as sourced

summarizer <- function(x){ #function to run rma on transformed biserial and correlations
  fitr <- rma(yi = x$r, vi = x$vi, data = x) #rma for biserial and pearson correlations (distinct per effect!)
  ci <- confint(fitr)$random[c(1, 3), ]
  data.frame(r = fitr$b[[1]], tau2 = fitr$tau2, tau2.lb = ci[1, 2], tau2.ub = ci[1, 3],
             I2 = fitr$I2, I2.lb = ci[2, 2], I2.ub = ci[2, 3]) 
}

#estimate tau2 for tranformed biserial and pearson's correlations
res2 <- dat2 %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(summarizer, .id = "effect")

>>>>

#estimate tau2 for tranformed biserial and pearson's correlations
#'summarizer' is a sourced function
res2 <- dat2 %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(summarizer, .id = "effect")
